%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Senior Software Engineer} % Job title
{Milwaukee Tool} % Organization
{Milwaukee, Wisconsin (Remote)} % Location
{Dec. 2024 - Current} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Directed development of novel integraton with an internal application including distributed transactions.}
    \item {Increased backend logic coverage by designing integration tests around a dotnet api.}
    \item {Led backend design, taking responsibility for backend design decisions on the team.}
    \item {Improved testing methodoligy by introducing Stubs in lieu of some Mocks.}
    \item {Skills: C\# \textbullet{} React \textbullet{} Tanstack Query, Router, Table \textbullet{} SQL Server \textbullet{} Integration testing \textbullet{} Clean Architecture}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Lead Software Engineer} % Job title
    {Dispute.com} % Organization
    {Milwaukee, Wisconsin (Remote)} % Location
    {Feb. 2023 - Sept. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected and developed secure, scalable systems resulting in 90\% reduction in time spent on 
                manual intervention in the core data pipeline.}
        \item {Onboarded and led a team of 3 developers towards a culture of communication and excellence.}
        \item {Introduced Auth0 for client authentication and authorization, automated management via Terraform.}
        \item {Directed development of a greenfield React application, encouraging best practices such as unit testing and component reuse.}
        \item {Created extensible system to manage integrations with CRMs and Chargeback Protection platforms (Konnektive, Sticky, Ethoca, Verifi)}
        \item {Created CI/CD pipelines in GitHub Actions which deployed applications via Terraform and released internal shared Nuget and NPM packages.}
        \item {Skills: C\# \textbullet{} Github Actions \textbullet{} React \textbullet{} Rust \textbullet{} App Service \textbullet{} SQL Server \textbullet{} Durable Functions \textbullet{} Application Insights \textbullet{} Entra Id/AAD}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Game Developer, Founder} % Job title
    {Fraculation LLC} % Organization
    {Milwaukee, Wisconsin} % Location
    {Sep. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Used C\# to implement a true-to-life Mendelian genetics system which faithfully recreates Punnet Square outcomes.}
        \item {Achieved high performance, processing 10,000s of entities every 10ms on consumer hardware as part of a tower defense game.}
        \item {Autogenerated C\# API from an OpenAPI specification with openapitools for use in Unity.}
        \item {Created open-source libraries leading to a 60\% reduction in code duplication across game jams.}
        \item {Built leaderboard API in Rust using Axum, Serde, HTMX, Sqlx, and Tokio.}
        \item {Skills: Unity \textbullet{} C\# \textbullet{} Rust \textbullet{} Real-time parallel algorithms \textbullet{} Data-oriented Design \textbullet{} ECS \textbullet{} DOTS \textbullet{} Jobs \textbullet{} Burst Compiler}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Unity Implementation Specialist} % Job title
    {Flite Golf \& Entertainment} % Organization
    {Milwaukee, Wisconsin (Remote)} % Location
    {Sep. 2022 - Feb. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided company-wide guidance on C\# and Unity best practices as the resident Unity expert.}
        \item {Introduced unit tests to an untested codebase.}
        \item {Introduced Azure Application Insights to capture logs across all facilities and deployments, decreasing time collecting logs in the field.}
        \item {Managed client relationships with the owner and employees of Luxe Golf, which hosted our applications.}
        \item {Led towards a culture of documentation by creating standardized test cases, a knowledge base, and an onboarding guide.}
        \item {Skills: Unity \textbullet{} C\# \textbullet{} QA Process Improvement \textbullet{} Azure App Insights}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {AWS Cloud Engineer} % Job title
    {Centare (Milwaukee Tool, One Key)} % Organization
    {Milwaukee, Wisconsin} % Location
    {Jan. 2021 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Used CQRS and Event Sourcing to build an ETL pipeline from SQL Server into Elasticsearch, ingesting millions of positional data points per day }
        \item {Learned AWS Lambda and the Kinesis Consumer Library in Python to build a serverless data pipeline}
        \item {Skills: Python \textbullet{} Terraform \textbullet{} Docker \textbullet{} C\# \textbullet{} AWS Lambda \textbullet{} Dynamodb \textbullet{} Kinesis}
      \end{cvitems}
 }

%---------------------------------------------------------
  \cventry
    {Full Stack Angular Developer} % Job title
    {Centare (Symplr Cactus)} % Organization
    {Milwaukee, Wisconsin} % Location
    {Sep. 2019 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Modernized existing web applications into Angular Single Page Applications.}
        \item {Onboarded two offshore teams to work inside the new project ecosystem.}
        \item {Mentored junior team members through pair programming and code reviews.}
        \item {Skills: Angular \textbullet{} Typescript \textbullet{} RxJS \textbullet{} Cypress \textbullet{} C\# Web API \textbullet{} Agile}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cloud Engineer, Angular Application Developer} % Job title
    {Centare (API Healthcare)} % Organization
    {Milwaukee, Wisconsin} % Location
    {Aug. 2017 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Converted legacy C\# on-premise modules to run on the Azure cloud.}
        \item {Managed automated build and deployment in Jenkins.}
        \item {Documented and led design decisions for Angular applications.}
        \item {Onboarded new team members to support Angular applications by creating a knowledge base and one-on-one mentoring}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {B.S. in Software Engineering} % Degree
    {MSOE} % Institution
    {Milwaukee, Wi} % Location
    { } % Date(s)
    {
      % \begin{cvitems} % Description(s) bullet points
      %   \item {Some stuff happened.}
      % \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
