%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior/Lead Software Engineer} % Job title
    {Dispute.com} % Organization
    {Milwaukee, Wisconsin (Remote)} % Location
    {Feb. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected and developed secure, scalable systems resulting in 90\% reduction in time spent on 
              manual intervention in the core data pipeline.}
        \item {Introduced Auth0 for client authentication and authorization, automated management via Terraform.}
        \item {Created extensible system to manage integrations with CRMs and Chargeback Protection platforms (Konnektive, Sticky, Ethoca, Verifi)}
        \item {Developed ingestion pipelines for unreliable data providers, decreasing the the need for manual intervention by 80\%.}
        \item {Prototyped Rust apis for high performance data processing.}
        \item {Created CI/CD pipelines in GitHub Actions which deployed applications via Terraform and released internal shared Nuget and NPM packages.}
        \item {Skills: C\# \textbullet{} Github Actions \textbullet{} Rust \textbullet{} App Service \textbullet{} Sql Server \textbullet{} Durable Functions \textbullet{} Application Insights \textbullet{} Entra Id/AAD}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Game Developer, Owner} % Job title
{Fraculation LLC} % Organization
{Milwaukee, Wisconsin} % Location
{Sep. 2021 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Created L-System interpretor to run custom mesh generation code performantly using Rust and Unity's DOTS.\@ Documented on my blog.}
    \item {Implemented a true-to-life Mendellian genetics system which faithfully recreates Punnet Square outcomes using C\#.}
    \item {Built an ECS system to simuilate over 10,000 3D enemies and projectiles in realtime at >60FPS as part of a tower defense game.}
    \item {Participated in 7 game jams between Jun 2023 and Aug 2024, reaching between top 3\% and 30\% ranking in each.}
    \item {Created open-source libraries leading to a 60\% reduction in code duplication across game jams. Addressing common needs such as Math, Save system, Logging, Scriptable variables, Leaderboards, and Unit Testing}
    \item {Used Async/Await to manage game and UI logic with a Task-based asynchronous pattern (TAP) in Unity.}
    \item {Built leaderboard API in Rust using Axum, Serde, HTMX, Sqlx, and Tokio.}
    \item {Autogenerated C\# API from an OpenAPI specification with openapitools for use in Unity.}
    \item {Skills: Unity \textbullet{} C\# \textbullet{} Rust \textbullet{} Real-time parallel algorithms \textbullet{} Data-oriented Design \textbullet{} ECS \textbullet{} DOTS \textbullet{} Jobs \textbullet{} Burst Compiler}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Unity Implementation Specialist} % Job title
    {Flite Golf \& Entertainment} % Organization
    {Milwaukee, Wisconsin (Remote)} % Location
    {Sep. 2022 - Feb. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided company-wide guidance on C\# and Unity best practices as the resident Unity expert.}
        \item {Reduced build times by 20\% restructuring project code into assembly definitons, enabling faster iteration times.}
        \item {Introduced unit tests to an untested codebase.}
        \item {Implemented extensible logging solution supporting both cloud-based analytics and local file logging.}
        \item {Introduced Azure Application Insights to capture logs across all facilities and deployments, decreasing time collecting logs in the field by 73\%.}
        \item {Managed on-site deployment of 36 Unity-based golf simulators, and Flite's client relationship with the independent facility.}
        \item {Built foundation for disciplined QA practice by designing standarized test cases.}
        \item {Led towards a culture of documentation and collaboration by creating a knowledge base and onboarding guide.}
        \item {Skills: Unity \textbullet{} C\# \textbullet{} QA Process Improvement \textbullet{} Azure App Insights}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {AWS Cloud Engineer} % Job title
    {Centare (Milwaukee Tool, One Key)} % Organization
    {Milwaukee, Wisconsin} % Location
    {Jan. 2021 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Used CQRS and Event Sourcing to build an ETL pipeline from Sql Server into Elasticsearch, ingesting millions of positional data points per day }
        \item {Learned AWS Lambda and the Kinesis Consumer Library in Python to build a serverless data pipeline}
        \item {Skills: Python \textbullet{} Terraform \textbullet{} Docker \textbullet{} C\# \textbullet{} AWS Lambda \textbullet{} Dynamodb \textbullet{} Kinesis}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Angular Developer} % Job title
    {Centare (Symplr Cactus)} % Organization
    {Milwaukee, Wisconsin} % Location
    {Sep. 2019 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Modernized existing web applications into Angular Single Page Applications.}
        \item {Onboarded two offshore teams to work inside the new project ecosystem.}
        \item {Skills: Angular \textbullet{} Typescript \textbullet{} RxJS \textbullet{} Cypress \textbullet{} C\# Web API \textbullet{} Agile}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cloud Engineer, Angular Application Developer} % Job title
    {Centare (API Healthcare)} % Organization
    {Milwaukee, Wisconsin} % Location
    {Aug. 2017 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Converted legacy C\# on-premise modules to run on the Azure cloud.}
        \item {Managed automated build and deployment in Jenkins.}
        \item {Worked on Time and Attendance software used by hospitals across US and Canada.}
        \item {Documented and led design decisions for Angular appliations.}
        \item {Worked in an organization of 6+ other teams.}
        \item {Onboarded new team members to support Angular applications by creating a knowledge base and one-on-one mentoring}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Development Intern} % Job title
    {Brady Corporation} % Organization
    {Milwaukee, Wisconsin} % Location
    {Jun. 2015 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created bespoke implementation of the Observer pattern for use in an AngularJS application.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
