%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
 {Senior/Lead Software Engineer} % Job title
 {Dispute.com} % Organization
 {Milwaukee, Wisconsin (Remote)} % Location
 {Feb. 2023 - Present} % Date(s)
 {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected and developed secure, scalable systems resulting in 90\% reduction in time spent on 
 manual intervention in the core data pipeline.}
        \item {Onboarded a team of 3 developers and led towards a culture of communication and excellence.}
        \item {Introduced Auth0 for client authentication and authorization, automated management via Terraform.}
        \item {Created extensible system to manage integrations with CRMs and Chargeback Protection platforms (Konnektive, Sticky, Ethoca, Verifi)}
        \item {Decreased the the need for manual intervention by 80\% in ingestion pipelines, resulting in faster and more reliable data processing.}
        \item {Created CI/CD pipelines in GitHub Actions which deployed applications via Terraform and released internal shared Nuget and NPM packages.}
        \item {Skills: C\# \textbullet{} Github Actions \textbullet{} Leadership \textbullet{} Rust \textbullet{} SQL Server \textbullet{} Durable Functions \textbullet{} Application Insights \textbullet{} Entra Id/AAD}
      \end{cvitems}
 }

%---------------------------------------------------------
  \cventry
 {Game Developer, Owner} % Job title
 {Fraculation LLC} % Organization
 {Milwaukee, Wisconsin} % Location
 {Sep. 2021 - Present} % Date(s)
 {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a true-to-life Mendelian genetics system which faithfully recreates Punnet Square outcomes using C\#.}
        \item {Built an ECS system to simulate over 10,000 3D enemies and projectiles in real time at >60FPS as part of a tower defense game.}
        \item {Developed reusable open-source libraries, reducing code duplication by 60\% across game jams. Addressing common needs such as Math, Save system, Logging, Scriptable variables, Leaderboards, and Unit Testing}
        \item {Used Async/Await to manage game and UI logic with a Task-based asynchronous pattern (TAP) in Unity.}
        \item {Built leaderboard API in Rust using Axum, Serde, HTMX, Sqlx, and Tokio.}
        \item {Autogenerated C\# API from an OpenAPI specification with openapitools for use in Unity.}
        \item {Skills: Unity \textbullet{} C\# \textbullet{} Team organization \textbullet{} Rust \textbullet{} Real-time parallel algorithms \textbullet{} Data-oriented Design \textbullet{} ECS \textbullet{} DOTS \textbullet{} Jobs \textbullet{} Burst Compiler}
      \end{cvitems}
 }

%---------------------------------------------------------
  \cventry
 {Unity Implementation Specialist} % Job title
 {Flite Golf \& Entertainment} % Organization
 {Milwaukee, Wisconsin (Remote)} % Location
 {Sep. 2022 - Feb. 2023} % Date(s)
 {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided company-wide guidance on C\# and Unity best practices as the resident Unity expert.}
        \item {Reduced build times by 20\% restructuring project code into assembly definitions, enabling faster iteration times.}
        \item {Introduced unit tests to an untested codebase.}
        \item {Integrated Azure Application Insights, decreasing log collection time by 73\%, significantly improving the troubleshooting process.}
        \item {Managed client relationships with the owner and employees of Luxe Golf, which hosted our applications.}
        \item {Led towards a culture of documentation by creating standardized test cases, a knowledge base, and an onboarding guide.}
        \item {Skills: Unity \textbullet{} C\# \textbullet{} QA Process Improvement \textbullet{} Azure App Insights}
      \end{cvitems}
 }

%---------------------------------------------------------
  \cventry
 {AWS Cloud Engineer} % Job title
 {Centare (Milwaukee Tool, One Key)} % Organization
 {Milwaukee, Wisconsin} % Location
 {Jan. 2021 - Jun. 2021} % Date(s)
 {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Used CQRS and Event Sourcing to build an ETL pipeline from SQL Server into Elasticsearch, ingesting millions of positional data points per day }
        \item {Learned AWS Lambda and the Kinesis Consumer Library in Python to build a serverless data pipeline}
        \item {Skills: Python \textbullet{} Terraform \textbullet{} Docker \textbullet{} C\# \textbullet{} AWS Lambda \textbullet{} Dynamodb \textbullet{} Kinesis}
      \end{cvitems}
 }

%---------------------------------------------------------
  \cventry
 {Full Stack Angular Developer} % Job title
 {Centare (API Healthcare)} % Organization
 {Milwaukee, Wisconsin} % Location
 {Sep. 2017 - Dec. 2020} % Date(s)
 {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Modernized existing web applications into Angular Single Page Applications, leading and documenting design decisions.}
        \item {Converted legacy C\# on-premise modules to run on the Azure cloud.}
        \item {Successfully onboarded and mentored two offshore teams, streamlining integration into the new project ecosystem and improving project delivery timelines.}
        \item {Mentored junior team members through pair programming, code reviews, and one-on-one mentoring.}
        \item {Managed automated build and deployment in Jenkins.}
        \item {Skills: Angular \textbullet{} Typescript \textbullet{} RxJS \textbullet{} Cypress \textbullet{} C\# Web API \textbullet{} Agile \textbullet{} Jenkins}
      \end{cvitems}
 }

%---------------------------------------------------------
  \cventry
 {IT Development Intern} % Job title
 {Brady Corporation} % Organization
 {Milwaukee, Wisconsin} % Location
 {Jun. 2015 - Dec. 2016} % Date(s)
 {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created bespoke implementation of the Observer pattern for use in an AngularJS application.}
      \end{cvitems}
 }

%---------------------------------------------------------
  \cventry
 {B.S. in Software Engineering} % Degree
 {MSOE} % Institution
 {Milwaukee, Wi} % Location
 {Sept. 2012 - May 2017} % Date(s)
 {
      % \begin{cvitems} % Description(s) bullet points
      %   \item {Some stuff happened.}
      % \end{cvitems}
 }

%---------------------------------------------------------
\end{cventries}
