%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------

%---------------------------------------------------------
 \cventry
  {\href{https://limeblossomjams.itch.io/the-last-storm-crystal}{https://limeblossomjams.itch.io/the-last-storm-crystal}} % Subheading
   {The Last Storm Crystal} % Project name
   {Brackeys Jam 2024.2} % Location
   {Sept. 2024, 7 days} % Date(s)
   {
     \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Leveraged and modified existing code to efficiently meet our needs without rewriting.}
      \item {Ensure the game and AI behaved correctly as large changes to the codebase were made through test-driven development.}
      \item {Skills: C\# \textbullet{} Test driven development \textbullet{} AI \textbullet{} Library development }
     \end{cvitems}
   }
 
%---------------------------------------------------------
  \cventry
   {\href{https://limeblossomjams.itch.io/the-essence-of-tactics}{https://limeblossomjams.itch.io/the-essence-of-tactics}} % Subheading
    {The Essence of Tactics} % Project name
    {Pirate Software Jam 15} % Location
    {Jul. 2024, 14 days} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a Tile-Tactics game with a game designer and artist, building on shared code from a previous jam.}
        \item {Created pathfinding and optimizing AI based on a custom fitness function.}
        \item {Skills: C\# \textbullet{} Data-driven design \textbullet{} Test driven development \textbullet{} AI \textbullet{} Library development }
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
  {\href{https://github.com/dsmiller95/fraculation-leaderboard}{https://github.com/dsmiller95/fraculation-leaderboard}} % Subheading
   {Leaderboard web app} % Project name
   {Hobby} % Location
   {Apr. 2024} % Date(s)
   {
     \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Created a web app with Rust and HTMX to store leaderboards of games I created.}
      \item {Allowed equivalent display of data between HTML and JSON MIME types without code or endpoint repetition.}
      \item {Skills: Rust \textbullet{} Axum \textbullet{} HTMX \textbullet{} Api development \textbullet{} SQL, SQLx }
     \end{cvitems}
   }

%---------------------------------------------------------
 \cventry
  {\href{https://github.com/dsmiller95/SplendorSimulator}{https://github.com/dsmiller95/SplendorSimulator}} % Subheading
   {Splendor Simulator} % Project name
   {Hobby} % Location
   {Dec. 2022} % Date(s)
   {
     \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed a Python application to train an AI to play the board game Splendor.}
      \item {Allowed display of game states during training with a Flask API and a React frontend.}
      \item {Partially completed migration of game logic to Rust to increase performance, binding to Python with pyo3/Maturin.}
      \item {Skills: Python \textbullet{} Pytorch \textbullet{} Flask \textbullet{} React \textbullet{} Rust \textbullet{} Pyo3 \textbullet{} React \textbullet{} Api development }
     \end{cvitems}
   }

%---------------------------------------------------------
  \cventry
   {\href{https://spikedevelops.itch.io/disconnect}{https://spikedevelops.itch.io/disconnect}} % Subheading
    {Disconnect} % Project name
    {Top 3\%, GMTK Jam 2023} % Location
    {Jun. 2023, 48 hours} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coordinated team of 3 software developers to rapidly collaborate without conflicts on a 48-hour timeline.}
        \item {Created a game with 0 logic bugs at launch through Test-Driven development when creating both game logic and AI.}
        \item {Skills: Leadership \textbullet{} Test driven development \textbullet{} C\#}
      \end{cvitems}
 }

%---------------------------------------------------------
  \cventry
   {\href{https://www.fraculation.com/blog/lindenmayer-implementation}{https://www.fraculation.com/blog/lindenmayer-implementation}} % Subheading
    {L-System Language Execution Engine} % Project name
    {Fraculation LLC} % Location
    {Dec. 2020 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A custom implementation of L-Systems including a tokenizer and a multithreaded interpreter.}
        \item {Built with Unity's Jobs system to enable multithreading, and rendered in Unity as Meshs.}
        \item {Presented at M+Dev in 2022.}
        \item {Experimented with Rust interoperability in Unity to improve performance.}
        \item {Skills: Unity \textbullet{} C\# \textbullet{} Rust \textbullet{} Developer Tooling \textbullet{} Library development  \textbullet{} Jobs \textbullet{} Burst Compiler \textbullet{} Multithreading \textbullet{} Performance Optimization}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
    