%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------

%---------------------------------------------------------
 \cventry
 {\href{https://limeblossomjams.itch.io/the-last-storm-crystal}{https://limeblossomjams.itch.io/the-last-storm-crystal}} % Subheading
 {The Last Storm Crystal} % Project name
 {Brackeys Jam 2024.2} % Location
 {Sept. 2024, 7 days} % Date(s)
 {
     \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Created a deck-building roguelike tactics game, building on top of a previous tactics game. Overhauling mechanics and creating new abilities.}
       \item {Leveraged and modified existing code to efficiently meet our needs without rewriting.}
       \item {Used test-driven development to ensure the game and AI behaved correctly as large changes to the codebase were made.}
      \item {Skills: C\# \textbullet{} Test driven development \textbullet{} AI \textbullet{} Library development }
     \end{cvitems}
 }

%---------------------------------------------------------
  \cventry
 {\href{https://limeblossomjams.itch.io/the-essence-of-tactics}{https://limeblossomjams.itch.io/the-essence-of-tactics}} % Subheading
 {The Essence of Tactics} % Project name
 {Pirate Software Jam 15} % Location
 {Jul. 2024, 14 days} % Date(s)
 {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a Tile-Tactics game with a game designer and artist, building on shared code from a previous jam.}
        \item {Employed Data-driven design by configuring all abilities via ScriptableObjects, exposing these tools to the game designer.}
        \item {Created pathfinding and optimizing AI based on a custom fitness function.}
        \item {Skills: C\# \textbullet{} Data-driven design \textbullet{} Test driven development \textbullet{} AI \textbullet{} Library development }
      \end{cvitems}
 }

%---------------------------------------------------------
  \cventry
 {\href{https://dsmiller95.itch.io/takoyaki-volleyball-club}{https://dsmiller95.itch.io/takoyaki-volleyball-club}} % Subheading
 {Takoyaki Volleyball Club} % Project name
 {Top 6\%, Pixel Jam} % Location
 {May. 2024, 8 days} % Date(s)
 {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked alone with two artist-designers to build a 2D action game.}
        \item {Cut down on time spent configuring prefabs by 75\% by developing extensive in-editor tooling to allow the designer to iterate rapidly.}
        \item {Created a distortion shader to simulate the effects of droplets in water.}
        \item {Modeled UI interactions with async/await and Task-based asynchronous pattern (TAP) in Unity.}
        \item {Skills: Communication \textbullet{} C\# \textbullet{} Data-driven design \textbullet{} Unity \textbullet{} Developer tooling }
      \end{cvitems}
 }

%---------------------------------------------------------
  \cventry
 {\href{https://github.com/dsmiller95/ludum-dare-54}{https://github.com/dsmiller95/ludum-dare-54}} % Subheading
 {Mosh Pint} % Project name
 {Top 13\%, Ludum Dare 54} % Location
 {Oct. 2023, 4 days} % Date(s)
 {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Organized team of 6 on a 4-day project.}
        \item {Learned Godot during the jam to create a novel top-down action puzzler game.}
        \item {Skills: Leadership \textbullet{} C\# \textbullet{} Godot \textbullet{} Active Learning}
      \end{cvitems}
 }

%---------------------------------------------------------
  \cventry
 {\href{https://spikedevelops.itch.io/disconnect}{https://spikedevelops.itch.io/disconnect}} % Subheading
 {Disconnect} % Project name
 {Top 3\%, GMTK Jam 2023} % Location
 {Jun. 2023, 48 hours} % Date(s)
 {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coordinated team of 3 software developers to rapidly collaborate without conflicts on a 48-hour timeline.}
        \item {Employed Test-Driven development when creating both game logic and AI, resulting in a game with 0 logic bugs at launch.}
        \item {Skills: Leadership \textbullet{} Test driven development \textbullet{} C\#}
      \end{cvitems}
 }

%---------------------------------------------------------
  \cventry
 {\href{https://www.fraculation.com/blog/lindenmayer-implementation}{https://www.fraculation.com/blog/lindenmayer-implementation}} % Subheading
 {L-System Language Execution Engine} % Project name
 {Fraculation LLC} % Location
 {Dec. 2020 - Jun. 2023} % Date(s)
 {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A custom implementation of L-Systems including a tokenizer and a multithreaded interpreter.}
        \item {Built with Unity's Jobs system to enable multithreading, and rendered in Unity as Meshs.}
        \item {Presented at M+Dev in 2022.}
        \item {Experimented with Rust interoperability in Unity to improve performance.}
        \item {Skills: Unity \textbullet{} C\# \textbullet{} Rust \textbullet{} Developer Tooling \textbullet{} Library development  \textbullet{} Jobs \textbullet{} Burst Compiler \textbullet{} Multithreading \textbullet{} Performance Optimization}
      \end{cvitems}
 }

%---------------------------------------------------------
\end{cventries}
    